This report is prepared for the Data Structures and Algorithms project by group 7 under the supervision of Mr. Nguyen Thanh Tinh. The work has been divided among team members, with their individual contributions outlined in the following table \ref{tab:work_assignment}:
\begin{table}[h!]
    \caption{Work assignment and contribution evaluation}
    \centering
    \begin{tabular}{|l|c|c|c|}
    \hline
    \textbf{Team Member} & \multicolumn{2}{|c|}{\textbf{Assigned Tasks}} & \textbf{Completion Rate (\%)}  \\ \hline
    \multirow{10}{*}{Thai Gia Huy} & \multirow{7}{*}{Report} & 1   & 100 \\ \cline{3-4}
                                  &                         & 2.2 & 100 \\ \cline{3-4}
                                  &                         & 3.3 & 100 \\ \cline{3-4}
                                  &                         & 4.2 & 100 \\ \cline{3-4}
                                  &                         & 5.3 & 100 \\ \cline{3-4}
                                  &                         & 6   & 100 \\ \cline{3-4}
                                  &                         & 8   & 100 \\ \cline{2-4}
                                  & \multirow{3}{*}{Slide}  & 3   & 100 \\ \cline{3-4}
                                  &                         & 4   & 100 \\ \cline{3-4}
                                  &                         & 5   & 100 \\ \cline{1-4}
    \multirow{9}{*}{Ho Thuy Tram} & \multirow{7}{*}{Report} & 2.1 & 100 \\ \cline{3-4}
                                  &                         & 3.1 & 100 \\ \cline{3-4}
                                  &                         & 3.2 & 100 \\ \cline{3-4}
                                  &                         & 4.1 & 100 \\ \cline{3-4}
                                  &                         & 5.1 & 100 \\ \cline{3-4}
                                  &                         & 5.2 & 100 \\ \cline{3-4}
                                  &                         & 7   & 100 \\ \cline{2-4}
                                  & \multirow{2}{*}{Slide}  & 1   & 100 \\ \cline{3-4}
                                  &                         & 2   & 100 \\ \cline{1-4}
    \end{tabular}
    
    \label{tab:work_assignment}
\end{table}

\vspace{10pt}

The report provides a comprehensive exploration of the LZW (Lempel-Ziv-Welch) compression algorithm, one of the most influential and widely used data compression techniques. The primary purpose of this report is to examine the theoretical foundations, practical applications, and performance characteristics of LZW, making it accessible to readers with an interest in data compression technologies.

\vspace{10pt}

The report begins with an introduction to the historical development of LZW and its significance in various real-world scenarios. It then delves into the algorithm's mechanics, outlining both the compression and decompression processes with illustrative examples to enhance understanding. Following this, the report analyzes the algorithm's performance, focusing on efficiency and how compression ratios influence time complexity. To place LZW in a broader context, the report provides an overview of related algorithms, such as LZ77 and LZ78, emphasizing their unique features and how they compare with LZW.
\vspace{10pt}

The report aims to offer a balanced view, covering both theoretical insights and practical implications. While every effort has been made to ensure the content is comprehensive and accurate, certain simplifications were adopted to maintain clarity and accessibility. Feedback and constructive suggestions for improvement are welcome as they will help refine this work further.